### 2012-08-21 paper_sean/abstract.tex
JMC: reworked abstract...also some edits to intro:

Evolving gaits for physical robots is a longstanding and still open challenge. 
While previous work has shown that evolutionary algorithms can outperform human engineers in generating gaits, in all of that work the experimenter has had to manually decide the regularities of the gaits. 
Such manual intervention is time consuming, requires expert knowledge, and adds constraints that may hurt performance. 
In this paper, we tested whether HyperNEAT -- a generative encoding that has shown to be able to automatically evolve a variety of high-performing regular gaits -- could generate gaits that could outperform manually designed, regularity-constrained, directly-encoded gaits. 
For our experiments, gaits were evolved in simulation and the final gait transferred to the real-world to evaluate the gait's actual performance.
The platform used was the QuadraTot, an open-source, 3D printed quadrupedal robot on which previous studies in gait evolution has already been done several times. 
In this study, we produced the fastest gait ever tried on this platform, outperforming the fastest published gait by 5.4\% with 20000 fewer evaluations run during gait generation. 
The gaits produced showed exploitation in regularity in simulation and real-world as was expected.

>>>>

% !TEX root =main.tex
Creating gaits for physical robots is a longstanding and still open challenge. 
%Evolutionary algorithms can outperform human engineers in generating such gaits, but this approach historically required engineers to manually decide which types of gaits would evolve. Such manual intervention is time consuming, requires expert knowledge, and adds constraints that may hurt performance. 
Recently, the HyperNEAT generative encoding was shown to automatically discover a variety of gait regularities, producing fast, coordinated gaits, but only for simulated robots. A follow-up study found that HyperNEAT did not produce impressive gaits when they evolved directly on a physical robot. A simpler encoding hand-tuned to produce regular gaits was tried on the same robot, and outperformed HyperNEAT, but these gaits were first evolved in simulation before being transferred to the robot. In this paper, we tested the hypothesis that the beneficial properties of HyperNEAT would outperform the simpler encoding if HyperNEAT gaits are first evolved in simulation before being transferred to reality. 
That hypothesis was confirmed, resulting in the fasted gaits yet observed for this robot. This result is important because it confirms that the early promise shown by generative encodings, specifically HyperNEAT, were not limited to evolving gaits in simulation, but indeed work on real robots.

%We further test whether gaits created by generative encodings such as HyperNEAT tend to be transferable from simulation to reality, which is an important question because the regularity-producing property of generative encodings should make the gap smaller. could generate gaits that could outperform manually designed, regularity-constrained, directly-encoded gaits. 
%
%For our experiments, gaits were evolved in simulation and the final gait transferred to the real-world to evaluate the gait's actual performance.
%The platform used was the QuadraTot, an open-source, 3D printed quadrupedal robot on which previous studies in gait evolution has already been done several times. 
%In this study, we produced the fastest gait ever tried on this platform, outperforming the fastest published gait by 5.4\% with 20000 fewer evaluations run during gait generation. 
%The gaits produced showed exploitation in regularity in simulation and real-world as was expected.

### 2012-08-21 paper_sean/introduction.tex
JMC: reworked abstract...also some edits to intro:

Legged locomotion provides several benefits over wheeled locomotion. 
A few examples of this are in flexibility in the type of terrain a robot could travel and in adapability to changes in a robot's physiology \cite{bongard:lipson}.
But designing a gait for a robot is often difficult and time consuming because the engineer must take into consideration many factors which must all fall into place for a successful gait pattern. 
Because of setbacks present in hand-designing gaits, evolving gaits using machine learning algorithms is an attractive and flexible approach that could be used for many different robot platforms with only a few tweaks.

>>>>

% !TEX root =main.tex
Legged locomotion provides several benefits over wheeled locomotion. 
A few examples of this are in flexibility in the type of terrain a robot could travel and in adapability to changes in a robot's physiology \cite{bongard:lipson}.
But designing a gait for a robot is often difficult and time consuming because the engineer must take into consideration many factors which must all fall into place for a successful gait pattern. 
Because of setbacks present in hand-designing gaits, evolving gaits with machine learning algorithms is an attractive and flexible approach that can automatically produce effective gaits for many different robot platforms with minimal human intervention.
